\documentclass{beamer}

\mode<presentation>
{
  \usetheme{Warsaw}
  \setbeamercovered{transparent}
}


\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}

\title{My Uml Paper}
\subtitle{How To Write Papers With Uml}
\author[Me]{Me Myself \ \texttt{me@myself.edu}}
\date[UML2015]{How To Make A Beamer With Plant Uml Pictures}
\subject{Plant Uml}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \tableofcontents
\end{frame}

\section{Finding My Way Around}

\subsection{First Steps}

\begin{frame}{How to itemize}
  	\begin{itemize}
  	    \item Approach one.
	  	\begin{itemize}
		    \item First dot.
		    \item Another.
	    \end{itemize}  	
  	    \item Approach two.
	  	\begin{itemize}
		    \item First dot.
		    \item Another.
	    \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}[fragile]{How to verbatimize}
	\begin{columns}
		\column{.5\textwidth}
			This program returns 0.
			\begin{verbatim}
int main()
{
    return 0;
}
			\end{verbatim}
		\column{.5\textwidth}
			This program returns 1.
			\begin{verbatim}
int main()
{
    return 1;
}
			\end{verbatim}
	\end{columns}
\end{frame}

\section{Our Results/Contribution}

\subsection{Main Results}

\begin{frame}{Make Titles Informative.}
\end{frame}

\subsection{Basic Ideas for Proofs/Implementation}

\begin{frame}{Make Titles Informative.}
\end{frame}

\section*{Summary}

\begin{frame}{Summary}

  % Keep the summary *very short*.
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}
  
  % The following outlook is optional.
  \vskip0pt plus.5fill
  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}



% All of the following is optional and typically not needed. 
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{For Further Reading}
    
  \begin{thebibliography}{10}
    
  \beamertemplatebookbibitems
  % Start with overview books.

  \bibitem{Author1990}
    A.~Author.
    \newblock {\em Handbook of Everything}.
    \newblock Some Press, 1990.
 
    
  \beamertemplatearticlebibitems
  % Followed by interesting articles. Keep the list short. 

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}

\end{document}


